# Problem 3 (25 points)

In this problem you will practice some basic R operations. Include solutions to each items by inserting a new R chunk of code (make sure you run the chunk so that the output is displayed)

(a) Create a variable called `my_name` that contains *your preferred name*.

(b) Create a variable called `name_length` that holds how many letters are in `my_name`.

(c) Show which value is bigger: $e^\pi$ or $\pi^e$. (Use the correct expressions for Euler's constant $e$ and the irrational number $\pi$ in R)

(d) Use the colon operator `:` to create a vector `v` of numbers from 31 to 86. Find the length of this vector using the `length()` function.

(e) Use the `seq()` function to produce a range of number from -5 to 10 in 0.5 increments.

```{r}
my_name <- "Cyler"
```

```{r}
name_length <- 5
```

```{r}
e <- 2.7183
pi <- 3.1416
sum1 = (e)^(pi)
sum2 = (pi)^(e)
print(sum1 - sum2)
print("e^pi is bigger")
```

```{r}
v <- 31:86
print(v)
length(v)
```

```{r}
seq(-5, 10, .5)
```

